This document contains two small examples of calling out from R to C++ to do
matrix multiplication.  The first example uses the `RcppArmadillo` package,
and the second uses the `RcppEigen` package.

The point here is mainly to get familiar with the mechanics of calling the C++
linear-algegra stuff from R, although the timing results are mildly
interesting as well.

Each example contains a timing comparison, comparing the built-in
matrix-multiplication function in R to the Rcpp* version.

In each case the C++ code is contained in a separate file and is executed
using the `sourceCpp` function in R.

Here is the first C++ function, **mat_mul_arma.cpp**:

```

#include <RcppArmadillo.h>

// [[Rcpp::depends(RcppArmadillo)]]

// [[Rcpp::export]]

arma::mat  mat_mul_arma(arma::mat A,
			arma::mat B) {
  arma::mat C = (A * B);
  return C;
}


/*** R

library(microbenchmark)
amat <- matrix(as.numeric(1:9),   nrow=3)
bmat <- matrix(as.numeric(10:18), nrow=3)

mat_mul_arma(amat, bmat)

amat %*% bmat

microbenchmark(
  amat %*% bmat,
  mat_mul_arma(amat, bmat)
)

bigMat1 <- matrix(runif(1000000), nrow=1000)
bigMat2 <- matrix(runif(1000000), nrow=1000)

all.equal(bigMat1 %*% bigMat2,
          mat_mul_arma(bigMat1, bigMat2))

microbenchmark(
  bigMat1 %*% bigMat2,
  mat_mul_arma(bigMat1, bigMat2)
)

*/

```

And here are the **results** for the `Armadillo` case:

```{r arma-example}

  library(Rcpp)
  sourceCpp("./mat_mul_arma.cpp")
  
```

Here is the second C++ function, **mat_mul_eigen.cpp**:

```

#include <RcppEigen.h>

// [[Rcpp::depends(RcppEigen)]]

// [[Rcpp::export]]

Eigen::MatrixXd  mat_mul_eigen(const Eigen::Map<Eigen::MatrixXd> A,
		               const Eigen::Map<Eigen::MatrixXd> B) {

  Eigen::MatrixXd C = (A * B);

  return C;
}


/*** R

library(microbenchmark)
amat <- matrix(as.numeric(1:9),   nrow=3)
bmat <- matrix(as.numeric(10:18), nrow=3)

mat_mul_eigen(amat, bmat)

amat %*% bmat

microbenchmark(
  amat %*% bmat,
  mat_mul_eigen(amat, bmat)
)

bigMat1 <- matrix(runif(1000000), nrow=1000)
bigMat2 <- matrix(runif(1000000), nrow=1000)

all.equal(bigMat1 %*% bigMat2,
          mat_mul_eigen(bigMat1, bigMat2))

microbenchmark(
    bigMat1 %*% bigMat2,
    mat_mul_eigen(bigMat1, bigMat2)
)

*/

```

And here are the **results** for the `Eigen` case:

```{r eigen-example}

  library(Rcpp)
  sourceCpp("./mat_mul_eigen.cpp")
  
```

